Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-30 docs/ms.tex
Update ms.tex

\section{Discussion}
\label{sec:XXX}

>>>>

\section{Discussion}
\label{sec:XXX}
In weak lensing survey,one way to btain high S/N ratio is to stack large number of lensing signal together,and 
calculate the mean shear map of all these lensing systems.However simply to stack allthe lensing signals would not be the
optimal way because of the amount of information we can obtain from each lensing system can be very different.
The Bayesian inference approach we proposed allows a natural way to optimally include all the data.What we need to do
is to propogate the whole likelihood of each lensing system while calculating the statistical properties of various lensing
systems.
